### 2012-11-25 paper.tex

\begin{table*}[htb]\centering
  \begin{tabular*}{\columnwidth}{@{}lllllll@{}}
      \toprule 
               &  TP Rate & FP Rate & Precision & Recall & F-Measure & Class \\   \midrule
               &  0.577   & 0.052   & 0.779     & 0.577  & 0.663     & >50K  \\   
               &  0.948   & 0.423   & 0.876     & 0.948  & 0.911     & <=50K \\   
Weighted Avg.  &  0.859   & 0.333   & 0.853     & 0.859  & 0.851     &       \\   \bottomrule
    \end{tabular*}
\caption{Random Forest -- 3 Random Features} 
\label{tab:adult:rand:3f}
\end{table*}
\FloatBarrier

>>>>

\begin{table*}[htb]\centering
  \begin{tabular*}{\columnwidth}{@{}lllllll@{}}
      \toprule 
               &  TP Rate & FP Rate & Precision & Recall & F-Measure & Class \\   \midrule
               &  0.577   & 0.052   & 0.779     & 0.577  & 0.663     & >50K  \\   
               &  0.948   & 0.423   & 0.876     & 0.948  & 0.911     & $\leq$50K \\   
Weighted Avg.  &  0.859   & 0.333   & 0.853     & 0.859  & 0.851     &       \\   \bottomrule
    \end{tabular*}
\caption{Random Forest -- 3 Random Features} 
\label{tab:adult:rand:3f}
\end{table*}
\FloatBarrier
